---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# neighborweights

## Overview

The `neighborweights` package provides a collection of functions for constructing adjacency matrices based on spatial and feature-based similarity between data points. It enables users to analyze and visualize complex data relationships by creating spatial and feature-weighted adjacency matrices using various methods.

## Installation

You can install the `neighborweights` package from GitHub with:

```r
# install.packages("devtools")
devtools::install_github("bbuchsbaum/neighborweights")
```

##Usage

Here's a basic example demonstrating how to create a spatial adjacency matrix using the spatial_adjacency function:

```{r}
library(neighborweights)

# Generate random coordinates
coord_mat <- matrix(runif(100), nrow=10, ncol=2)

# Calculate the spatial adjacency matrix
spatial_mat <- spatial_adjacency(coord_mat, nnk=5, sigma=1)

# Inspect the resulting matrix
print(spatial_mat)
```


For more advanced usage and additional examples, please refer to the package documentation and vignettes (coming soon).




